# Chapter 3

```{r echo=FALSE, message=FALSE, warning=FALSE, Load_packages}

library(fpp2)

```

1. For the following series, find an appropriate Box-Cox transformation in order to stabilize the variance.

```{r echo=FALSE, message=FALSE, warning=FALSE, Question1}

# - usnetelec
lambda_usnetelec <- BoxCox.lambda(usnetelec)
print(c("Good value of lambda for usnetelec: ", 
        lambda_usnetelec))
autoplot(BoxCox(usnetelec, lambda_usnetelec))

# - usgdp
lambda_usgdp <- BoxCox.lambda(usgdp)
print(c("Good value of lambda for usgdp: ", 
      lambda_usgdp))
autoplot(BoxCox(usgdp, lambda_usgdp))

# - mcopper
lambda_mcopper <- BoxCox.lambda(mcopper)
print(c("Good value of lambda for mcopper: ", 
      lambda_mcopper))
autoplot(BoxCox(mcopper, lambda_mcopper))

# - enplanements
lambda_enplanements <- BoxCox.lambda(enplanements)
print(c("Good value of lambda for enplanements: ", 
      lambda_enplanements))
autoplot(BoxCox(enplanements, lambda_enplanements))

```


2. Why is a Box-Cox transformation unhelpful for the cangas data?

```{r echo=FALSE, message=FALSE, warning=FALSE, Question2}

autoplot(cangas)

lambda_cangas <- BoxCox.lambda(cangas)
autoplot(BoxCox(cangas, lambda_cangas))
# can see that Box-Cox transformation doesn't yield simpler model

```

3. What Box-Cox transformation would you select for your retail data (from Exercise 3 in Section 2.10)?

```{r echo=FALSE, message=FALSE, warning=FALSE, Question3}

retaildata <- xlsx::read.xlsx("retail.xlsx", sheetIndex = 1, startRow = 2)
myts <- ts(retaildata[,"A3349873A"], frequency=12, start=c(1982,4))

lambda_retail <- BoxCox.lambda(myts)
print(c("selected lambda:", lambda_retail))

fc_retail <- rwf(myts, 
                 drift = TRUE, 
                 lambda = lambda_retail,
                 h = 50,
                 level = 80)

fc_retail_biasadj <- rwf(myts, 
                         drift = TRUE, 
                         lambda = lambda_retail,
                         h = 50,
                         level = 80,
                         biasadj = TRUE)

autoplot(myts) +
  autolayer(fc_retail, series = "Simple Back Transform") +
  autolayer(fc_retail_biasadj$mean, series = "Bias Adjusted") +
  guides(colour = guide_legend(title = "Forecast"))
# It would be better to choose bias adjusted Box-Cox Transformation with lambda = 0.128

```

4. For each of the following series, make a graph of the data. If transforming seems appropriate, do so and describe the effect. dole, usdeaths, bricksq.

```{r echo=FALSE, message=FALSE, warning=FALSE, Question4}

autoplot(dole)
lambda_dole <- BoxCox.lambda(dole)
autoplot(BoxCox(dole, lambda_dole))
# For dole data, it looked like using Box-Cox Transformation would be better to see the pattern

autoplot(usdeaths)
lambda_usdeaths <- BoxCox.lambda(usdeaths)
autoplot(BoxCox(usdeaths, lambda_usdeaths))
# For usdeaths data, it looked like it is meaningless to transform it

autoplot(bricksq)
lambda_bricksq <- BoxCox.lambda(bricksq)
autoplot(BoxCox(bricksq, lambda_bricksq))
# For bricksq data, it looked like it is meaningless to transform it

```


5. Calculate the residuals from a seasonal naïve forecast applied to the quarterly Australian beer production data from 1992. Test if the residuals are white noise and normally distributed. What do you conclude?

```{r echo=FALSE, message=FALSE, warning=FALSE, Question5}

beer <- window(ausbeer, start=1992)
fc <- snaive(beer)
autoplot(fc)
res <- residuals(fc)
autoplot(res)

checkresiduals(fc)

# When just see the result of ACF, it looked like the residuals aren't white noise because of 4-lagged value. And Ljung-Box test shows that it is statistically signigicant. Therefore they aren't white noise. Also they aren't normally distributed.

```


6. Repeat the exercise for the WWWusage and bricksq data. Use whichever of naive or snaive is more appropriate in each case.

7. Are the following statements true or false? Explain your answer.

 a. Good forecast methods should have normally distributed residuals.
 b. A model with small residuals will give good forecasts.
 c. The best measure of forecast accuracy is MAPE.
 d. If your model doesn't forecast well, you should make it more complicated.
 e. Always choose the model with the best forecast accuracy as measured on the test set.

8. For your retail time series (from Exercise 3 in Section 2.10):

 a. Split the data into two parts using

myts.train <- window(myts, end=c(2010,12))
myts.test <- window(myts, start=2011)

 b. Check that your data have been split appropriately by producing the following plot.

autoplot(myts) + 
  autolayer(myts.train, series="Training") +
  autolayer(myts.test, series="Test")

 c. Calculate forecasts using snaive applied to myts.train.

fc <- snaive(myts.train)

 d. Compare the accuracy of your forecasts against the actual values stored in myts.test.

accuracy(fc,myts.test)
 
 e. Check the residuals.

checkresiduals(fc)

Do the residuals appear to be uncorrelated and normally distributed?

 f. How sensitive are the accuracy measures to the training/test split?

9. vn contains quarterly visitor nights (in millions) from 1998-2015 for eight regions of Australia.

 a. Use window() to create three training sets for vn[,"Melbourne"], omitting the last 1, 2 and 3 years; call these train1, train2, and train3, respectively. For example train1 <- window(vn[, "Melbourne"], end = c(2014, 4)).

 b. Compute one year of forecasts for each training set using the snaive() method. Call these fc1, fc2 and fc3, respectively.

 c. Use accuracy() to compare the MAPE over the three test sets. Comment on these.

10. Use the Dow Jones index (data set dowjones) to do the following:

 a. Produce a time plot of the series.
 b. Produce forecasts using the drift method and plot them.
 c. Show that the forecasts are identical to extending the line drawn between the first and last observations.
 d. Try using some of the other benchmark functions to forecast the same data set. Which do you think is best? Why?

11. Consider the daily closing IBM stock prices (data set ibmclose).

 a. Produce some plots of the data in order to become familiar with it.
 b. Split the data into a training set of 300 observations and a test set of 69 observations.
 c. Try using various benchmark methods to forecast the training set and compare the results on the test set. Which method did best?
 d. Check the residuals of your preferred method. Do they resemble white noise?

12. Consider the sales of new one-family houses in the USA, Jan 1973 - Nov 1995 (data set hsales).

 a. Produce some plots of the data in order to become familiar with it.
 b. Split the hsales data set into a training set and a test set, where the test set is the last two years of data.
 c. Try using various benchmark methods to forecast the training set and compare the results on the test set.  Which method did best?
 d. Check the residuals of your preferred method. Do they resemble white noise?