# Chapter 6

```{r echo=FALSE, message=FALSE, warning=FALSE, Load_packages}

library(fpp2)
library(seasonal)

```

2. The plastics data set consists of the monthly sales (in thousands) of product A for a plastics manufacturer for five years.

```{r echo=FALSE, message=FALSE, warning=FALSE, Question2}

# a. Plot the time series of sales of product A. Can you identify seasonal fluctuations and/or a trend-cycle?
autoplot(plastics)
# plot of the data shows that there are seasonal fluctuation and upward trend.

# b. Use a classical multiplicative decomposition to calculate the trend-cycle and seasonal indices.
decompose_plastics <- decompose(plastics,
                                type = "multiplicative")

autoplot(decompose_plastics)

# c. Do the results support the graphical interpretation from part (a)?
# Yes.

# d. Compute and plot the seasonally adjusted data.
autoplot(plastics, series="Data") +
  autolayer(trendcycle(decompose_plastics), series="Trend") +
  autolayer(seasadj(decompose_plastics), series="Seasonally Adjusted") +
  xlab("Year") + ylab("Monthly Sales amount") +
  ggtitle("Sales of plastic product (in thousand)") +
  scale_colour_manual(values=c("gray","blue","red"),
                     breaks=c("Data","Seasonally Adjusted","Trend"))

# e. Change one observation to be an outlier (e.g., add 500 to one observation), and recompute the seasonally adjusted data. What is the effect of the outlier?
plastics_new <- plastics
plastics_new[20] <- plastics_new[20] + 500
decompose_plastics_new <- decompose(
  plastics_new,
  type = "multiplicative"
  )

autoplot(plastics_new, series = "Data") +
  autolayer(trendcycle(decompose_plastics_new),
            series = "Trend") +
  autolayer(seasadj(decompose_plastics_new),
            series = "Seasonally Adjusted") +
  xlab("Year") + ylab("Monthly Sales amount") +
  ggtitle("Sales of plastic projuct with outlier") +
  scale_color_manual(values=c("gray", "blue", "red"),
                     breaks=c("Data", "Seasonally Adjusted", "Trend"))
# The outlier affect trend little, but affect seasonally adjusted data severely. Seasonally adjusted data has error as original data has.

# f. Does it make any difference if the outlier is near the end rather than in the middle of the time series?
plastics_new[55] <- plastics_new[55] + 500
decompose_plastics_new <- decompose(
  plastics_new,
  type = "multiplicative"
  )

autoplot(plastics_new, series = "Data") +
  autolayer(trendcycle(decompose_plastics_new),
            series = "Trend") +
  autolayer(seasadj(decompose_plastics_new),
            series = "Seasonally Adjusted") +
  xlab("Year") + ylab("Monthly Sales amount") +
  ggtitle("Sales of plastic projuct with outliers") +
  scale_color_manual(values=c("gray", "blue", "red"),
                     breaks=c("Data", "Seasonally Adjusted", "Trend"))

# If an outlier is near the end, the effect to trend decreases.
```


3. Recall your retail time series data (from Exercise 3 in Section 2.10). Decompose the series using X11. Does it reveal any outliers, or unusual features that you had not noticed previously?

```{r echo=FALSE, message=FALSE, warning=FALSE, Question3}
# Load retail.xlsx data
library(xlsx)
retail <- read.xlsx("retail.xlsx", 
                    sheetIndex = 1,
                    startRow = 2)
head(retail)

# change the retail data to ts object
ts_retail <- ts(retail[,"A3349873A"], 
                frequency=12, 
                start=c(1982,4))

# plot the data to see if there is a trend or seasonality.
autoplot(ts_retail)
# There are trend and seasonality.

# Decompose the series using X11.
x11_retail <- seas(ts_retail, x11 = "")

autoplot(x11_retail)
# there were some outliers that I didn't expect. Especially the biggest outlier happened in 2001. And I didn't expect the seasonality effect decreases as trend increases.

```

4. The result of decomposing the number of persons in the civilian labor force in Australia each month from February 1978 to August 1995 are shown below.

```{r echo=FALSE, message=FALSE, warning=FALSE, Question4_Figures}

# Below figures aren't same with the originals.

# First figure: Decomposition of the number of persons in the civilian labor force in Australia each month from February 1978 to August 1995.
library(seasonal)
library(fpp2)

x11_labour <- seas(labour, x11 = "")

autoplot(x11_labour) + xlab("Year") +
  ggtitle("Classical additive decomposition of civilian labour force")

# Second figure: ggsubseries plot of civilian labor force.
ggsubseriesplot(seasonal(x11_labour)) +
  ylab("Seasonal")

```

a. Write about 3-5 sentences describing the results of the seasonal adjustment. Pay particular attention to the scales of the graphs in making your interpretation.
b. Is the recession of 1991/1992 visible in the estimated components?

5. This exercise uses the cangas data (monthly Canadian gas production in billions of cubic metres, January 1960 - February 2005).
a. Plot the data using autoplot, ggsubseriesplot and ggseasonplot to look at the effect of the changing seasonality over time. What do you think is causing it to change so much?
b. Do an STL decomposition of the data. You will need to choose s.window to allow for the changing shape of the seasonal component.
c. Compare the results with those obtained using SEATS and X11. How are they different?

6. We will use the bricksq data (Australian quarterly clay brick production. 1956-1994) for this exercise.
a. Use an STL decomposition to calculate the trend-cycle and seasonal indices. (Experiment with having fixed or changing seasonality.)
b. Compute and plot the seasonally adjusted data.
c. Use a naïve method to produce forecasts of the seasonally adjusted data.
d. Use stlf to reseasonalize the results, giving forecasts for the original data.
e. Do the residuals look uncorrelated?
f. Repeat with a robust STL decomposition. Does it make much difference?
g. Compare forecasts from stlf with those from snaive, using a test set comprising the last 2 years of data. Which is better?

7. Use stlf to produce forecasts of the writing series with either method="naive" or method="rwdrift", whichever is most appropriate. Use the lambda argument if you think a Box-Cox transformation is required.

8. Use stlf to produce forecasts of the fancy series with either method="naive" or method="rwdrift", whichever is most appropriate. Use the lambda argument if you think a Box-Cox transformation is required.

### Question 1 is related with math, not related with coding that I didn't include them in here.